ODGI: understanding pangenome graphs

### 2021-10-29 manuscript/main.tex
specify where we use odgi position

In addition to these projections, we use the paths in the graph to provide a universal coordinate space.
It also supports several kinds of ``lift-over'' of coordinates between different genomes.
These allow for the direct translation of single coordinates and ranges, in an interactive way.
And, they let us extract a pairwise 1:many alignment between a given set of ``query'' sequences and a given set of ``target'' or reference sequences.
This lets us convert the graph to lift-over maps compatible with standard software for projecting annotations and alignments from one genome to another.

@@

Figure showing the untangling of C4 ?
Figure showing tips over a single human chromosome from HPRC.

>>>>

In addition to these projections, we use the paths in the graph to provide a universal coordinate space.
It also supports several kinds of ``lift-over'' of coordinates between different genomes (Fig. \ref{fig:odgi_viz}\textbf{f-g}).
These allow for the direct translation of single coordinates and ranges, in an interactive way.
And, they let us extract a pairwise 1:many alignment between a given set of ``query'' sequences and a given set of ``target'' or reference sequences.
This lets us convert the graph to lift-over maps compatible with standard software for projecting annotations and alignments from one genome to another.

@@

Figure showing the untangling of C4 (Fig. \ref{fig:odgi_viz}\textbf{f-g})
Figure showing tips over a single human chromosome from HPRC.
